\cleardoublepage

\chapter*{Glossary}

\pagestyle{plain}

\begin{description}
\item[ADC] Analogue to Digital Converter.
\item[Beam Pulse] Bunch train. Usually referring to the 1.2~\(\mathrm{\mu s}\), 3~GHz bunch train at CTF3.
\item[BPM] Beam Position Monitor.
\item[CLEX] CLIC Experimental Area at CTF3.
\item[CLIC] Compact Linear Collider.
\item[BDS] Beam Delivery System.
\item[CR] Combiner Ring.
\item[Diode] The power dependent output signal from the phase monitor electronics.
\item[DAC] Digital to Analogue Converter.
\item[DAQ] Data Acquisition system, usually referring to the LabVIEW application used to control the FONT5a board.
\item[DL] Delay Loop.
\item[Downstream Phase] Phase measured by Mon~3 in the TBL line, after the correction chicane.
\item[Energy or Energy Spread] Unless otherwise stated, the fractional momentum error or offset, \(\Delta p/p_0\), of the beam from the nominal design momentum, \(p_0\).
\item[FONT5a Board] Digital PFF controller, provided by Oxford University.
\item[CT Line] Beam line connecting the linac and TL1 at CTF3. Where the upstream phase monitors are installed.
\item[CTF3] CLIC Test Facility 3.
\item[Jitter] RMS variation about the mean.
\item[LO] Local Oscillator. The 12~GHz reference phase used by the phase monitor electronics.
\item[Mean Pulse Phase] Mean phase of one beam pulse, usually restricted to a several hundred nanosecond central part of the pulse.
\item[Mean Phase Jitter] The standard deviation of the mean pulse phases, across all the beam pulses in a dataset.
\item[Mixer] The phase dependent output signal from the phase monitor electronics.
\item[Phase] Time of arrival with respect to the reference particle, expressed in terms of a phase at 12~GHz (for the purposes of this thesis). 360 degrees at 12~GHz is around 80~ps.
\item[Phase Along the Pulse] The variation in phase across one beam pulse.
\item[Phase Jitter Along the Pulse] The standard deviation of the phase values at one specific point in the beam pulse, taken across all the pulses in a dataset.
\item[PFF] Phase Feedforward.
\item[Resolution] When referring to the phase monitors, the instrumental uncertainty of the measurement.
\item[RF] Radio Frequency. Usually referring to the RF power used to accelerate the CLIC beams, or beam induced signal from the phase monitors used as the ``RF'' input to the phase monitor electronics.
\item[RMS] Root-mean-square.
\item[TBL] Test Beam Line at CTF3 in CLEX. Where the downstream phase monitor is installed.
\item[TL1] Transfer line between the delay loop exit and the combiner ring entrance at CTF3.
\item[TL2] Transfer line between the combiner ring exit and CLEX at CTF3. Contains the PFF correction chicane.
\item[Upstream Phase] Phase measured by either Mon~1 or Mon~2 in the CT line. Used as the PFF input.

\item[\(\phi_{u}\), \(\phi_{1}\) or \(\phi_{2}\)] Upstream phase (measured in either Mon~1 or Mon~2).
\item[\(\phi_{d}\) or \(\phi_{3}\)] Downstream phase.
\item[\(\sigma_{u}\)] Upstream phase jitter.
\item[\(\sigma_{d}\)] Downstream phase jitter.
\item[\(\rho_{ud}\)] Correlation between the upstream and downstream phase.
\item[\(\rho_{up}\)] Correlation between the upstream phase and the beam energy.
\item[\(\rho_{dp}\)] Correlation between the downstream phase and the beam energy.
\item[\(R_{56}\)] First order transfer matrix coefficient describing the dependence of the phase on the beam energy.
\item[\(T_{566}\)] Transfer matrix coefficient describing the second order dependence of the phase on the beam energy.
\end{description}

